%
% Export to PDF (LaTeX):
%   xelatex resume.tex
% or: latexmk -xelatex -pdf resume.tex
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\bfseries}{}{0pt}{}
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black}

\begin{document}
{\LARGE \textbf{Matt Hartnett}}\\[4pt]
\textbf{Email:} \href{mailto:matthew.e.hartnett@gmail.com}{matthew.e.hartnett@gmail.com} \quad
\textbf{GitHub:} \href{https://github.com/hartnettmatt}{github.com/hartnettmatt} \quad
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/hartnettmatt}{linkedin.com/in/hartnettmatt}

\section*{Skills}
\begin{itemize}[leftmargin=*]
\item \textbf{Digital Design:} SystemVerilog RTL, Vivado, DSP, tcl, VHDL, Quartus, Libero
\item \textbf{Digital Verification:} SystemVerilog TB, Cocotb, Verilator, xsim, Modelsim
\item \textbf{Circuit Design and Analysis:} LTSpice, Advanced Design System, Soldering, Solidworks Electrical, DipTrace, Eagle
\item \textbf{Software Development:} Python, C++, Embedded C, Java
\item \textbf{Linux Development:} Ubuntu, Fedora, Buildroot, Yocto, PetaLinux
\item \textbf{Embedded Programming:} Embedded C, Codasip, Arduino, Raspberry Pi
\item \textbf{Web Development:} HTML, CSS, Javascript, PHP, SQL
\item \textbf{Software Systems:} Git, CI/CD, Matlab, Simulink Real-time, OpenCV, SVN
\item \textbf{General:} Debugging and problem solving for all architectures listed above
\item \textbf{Project Management Tools:} Agile PLM, Confluence, DOORS NG, OpenText MBPM
\end{itemize}

\section*{Experience}
\subsection*{Embedded Systems Engineer --- FIRST RF \hfill Boulder \quad 10/2024--Present}
\begin{itemize}[leftmargin=*]
\item Architected and implemented the full FPGA/HDL stack for a production radar system, owning design from module-level RTL to system integration (SystemVerilog, Vivado).
\item Delivered a new DSP pipeline that increased usable bandwidth 4$\times$, improved SNR by $\sim$20 dB, reduced logic utilization, and lowered end-to-end latency; modeled algorithms in Python/NumPy and verified with exhaustive testbenches.
\item Engineered a cycle-accurate, latency-constrained data path to meet strict radar timeline requirements; performed both simulation-based and on-hardware validation in partnership with embedded/software teams.
\item Modernized the internal HDL build system, enabling Verilator + cocotb flows; authored FIRST RF’s first cocotb testbenches and led full team adoption.
\end{itemize}

\subsection*{Electrical Engineer II --- Laboratory for Atmospheric and Space Physics \hfill CU Boulder \quad 06/2022--10/2024}
\begin{itemize}[leftmargin=*]
\item Designed high reliability test equipment for the \textbf{Libera} scientific mission.
\item Built systems from the ground up, including hardware, firmware, and software.
\item Operated with minimal oversight as the cognizant engineer for multiple projects.
\end{itemize}

\subsection*{Electrical Engineering Intern --- Laboratory for Atmospheric and Space Physics \hfill CU Boulder \quad 01/2021--06/2022}
\begin{itemize}[leftmargin=*]
\item Wrote low-level, hardware interface flight software for the \textbf{SPRITE} cubesat mission.
\item Developed an FPGA solution to test the scientific instrument on the ground.
\item Wrote an image compression algorithm that reduced the scientific data to 1/10th.
\end{itemize}

\subsection*{Teaching Assistant --- Circuits 1 for Engineers \hfill CU Boulder \quad 08/2021--12/2021}
\begin{itemize}[leftmargin=*]
\item Provided support to students in lab and in office hours.
\item Graded lab reports and created answer keys.
\item Developed midterm questions and helped course organization.
\end{itemize}

\subsection*{IT Technician --- Leeds School of Business \hfill CU Boulder \quad 01/2020--01/2021}
\begin{itemize}[leftmargin=*]
\item Installed and configured hardware and software for workstations and classrooms.
\item Communicated technical information through emails and phone calls.
\end{itemize}

\subsection*{Robotics Research Assistant --- Advanced Robotics Perception Group \hfill CU Boulder \quad 09/2019--05/2020}
\begin{itemize}[leftmargin=*]
\item Worked with a large team building a complex navigation robot.
\item Used OpenCV for object detection and identification, specifically heat signatures of human dummies, phones, and vents with $>80\%$ accuracy.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
\item \textbf{MSEE, Embedded Systems Engineering (In Progress)} --- University of Colorado Boulder \hfill 08/2023--Present, Boulder, CO
\item \textbf{BS, Electrical and Computer Engineering} --- University of Colorado Boulder \hfill 08/2019--05/2022, Boulder, CO
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
\item \textbf{Skyler Phased Array RADAR} --- Designed the end-to-end DSP chain and datapath (filtering, decimation/interpolation, mixing, 1 Gb/s Ethernet framing), then implemented cycle-accurate RTL with thorough TB coverage. Built a layered verification strategy (SystemVerilog TB + cocotb on Verilator) to catch interface, timing, and algorithmic defects early; mirrored tests on hardware for parity. Drove cross-functional integration and bring-up with embedded and application software, closing timing on high utilization designs, while meeting radar timeline constraints.
\item \textbf{Libera SSIM} --- Led the design of an advanced, high reliability test fixture utilized to validate the performance of the Libera instrument. Created a test rack to simulate the JPSS-3 spacecraft with 100\% of interfaces accurately recreated to maximize ``Test as you fly'' ideology. High reliability system that included a precisely synchronized FPGA with less than 10 ns of timing error.
\item \textbf{Libera EL Lifetest} --- Prepared and implemented the test bed for a 5-year-long, pre-flight motor verification test. Required a custom PCB as well as several custom harnesses to integrate dozens of components into a cohesive system.
\item \textbf{Senior Design Capstone (FRANKLIN)} --- Team lead for a phase coherent remote sensing system; primarily developed FPGA-based data collection and storage.
\item \textbf{GSE Detector Readout} --- Utilized an FPGA to read data from the scientific detector at full speed and then write that data over 100 Mb/s Ethernet to a PC for a live readout. Implemented a MicroBlaze processor on a Spartan-7 FPGA to run the TCP stack in C.
\item \textbf{3D Drone Mapping Simulation} --- Utilized the Webots simulation software to autonomously map in 3D; a drone sought out unmapped areas using a rapidly-exploring random tree.
\item \textbf{5-Stage RISC-V Processor} --- A fully functional and validated processor, built in Codasip using C++ and adapted into RTL as a synthesizable core with IO management, access to off-chip RAM, and 100\% verification; designed from the ground up to include the full ISA as well as ECC memory.
\end{itemize}

\section*{References}
\begin{itemize}[leftmargin=*]
\item \textbf{Dominic Doty} --- Software Development Engineer, Amazon --- \texttt{doty.dominic@gmail.com} --- (303) 704-8313
\item \textbf{Jack Williams, PhD} --- Senior Electrical Engineer, Blue Canyon Technologies --- (303) 735-8727
\end{itemize}

\end{document}
